The Circumnuclear Media and Accetion Rates of Quiescent Supermassive Black Holes

### 2015-02-08 ms.tex
2.1 update

A galaxy model is fully specified by four parameters: $\Mbh$,
$\Gamma$, $r_b$, and $\beta$.  We compute models for three different
black hole masses, $\Mbh = 10^6$, $10^7$, $10^8 \Msun$.  The
distribution of $\Gamma$ in the \citet{LauerFaber+:2007a} sample is
bimodal, with a concentration of ``core" galaxies with $\Gamma \lsim
0.3$ and a concentration of ``cusp" galaxies with $\Gamma \gsim 0.7$.
We bracket these possibilities by considering models with $\Gamma=0.8$
and $\Gamma=0.1$.  We fix $\beta = 2$ (a typical value) because our results are most sensitive to the
properties of the gas flow on radial scales $\ll r_b$ and do not depend sensitively on the outer power law slope of the stellar density profile. However, the presence of $\rb$ is necessary for to obtain a converged steady state for some regions of our parameter space.  Depending on the model, we
consider up to four different values of the $\rb$: 50 pc, 100 pc, 200 pc,
and 400 pc, a range motivated by the observed break radii in
the \citet{LauerFaber+:2007a} sample. For the core galaxies ($\Gamma \le$0.3) in this sample the break radius follows the scaling relationship $\rb\sim 106 \, (\Mbheight)^{0.39}$ pc, with scatter of
approximately one dex. Most the cusp ($\Gamma \ge0.5$) galaxies have
$\rb$ between 100 and 1000 pc, without a clear trend with $\Mbh$. {\bf AG: In practice when it is clear the rb will not have a
  significant effect on rs it may not be necessary to do runs. For
  instance for Mbh=$10^8$ Msun, gamma=0.8, and vw0=600 km/s the
  stagnation radius changes by only 8\%. So for cusp galaxies with
  vw0$\gsim$600 km/s and Mbh$\lsim 10^8$ Msun it seems like it is a
  safe bet to neglect the effect of the break radius on the
  solution. For low heating rates it my be difficult to converged
  solution for large values of rb=200 and 400 pc.}
% However, the presence of $\rb$ is necessary for to obtain a
% converged steady state for some regions of our parameter space. We
% adopt $\rb=100$ pc for cusp galaxies ($\Gamma=0.8$), while for core
% galaxy models we employ the scaling relation $\rb = $, motivated again
% by the \citet{LauerFaber+:2007a} sample. ({\bf BDM: fill in!}).
% Though simplistic, our results are not sensitive to our assumption
% about the value of $\rb$.

>>>>

A galaxy model is fully specified by four parameters: $\Mbh$,
$\Gamma$, $r_b$, and $\beta$.  We compute models for three different
black hole masses, $\Mbh = 10^6$, $10^7$, $10^8 \Msun$.  The
distribution of $\Gamma$ in the \citet{LauerFaber+:2007a} sample is
bimodal, with a concentration of ``core" galaxies with $\Gamma \lsim
0.3$ and a concentration of ``cusp" galaxies with $\Gamma \gsim 0.7$.
We bracket these possibilities by considering models with $\Gamma=0.8$
and $\Gamma=0.1$.

We fix $\beta = 2$ (a typical value) because our results are generally not sensitive to the
properties of the gas flow on radial scales $\gtrsim r_b$. The presence of the break radius $r_{b}$ is, however, necessary to obtain a converged steady state for some regions of our parameter space.  We consider solutions calculated for up to four values of $\rb$: 50 pc, 100 pc, 200 pc, and 400 pc, motivated by the range of break radii from the \citet{LauerFaber+:2007a} sample.\footnote{For the core galaxies the break radius follows the scaling relationship $\rb\sim 106 \, (\Mbheight)^{0.39}$ pc, with scatter of approximately one dex.  Most the cusp galaxies have
$\rb$ between 100 and 1000 pc, without a clear trend with $\Mbh$.}  In practice we calculate solutions for a range of $\rb$ only in cases when its precise value is expected to have a significant affect on the solution, in particular for high SMBH masses and low heating rates, for which the stagnation radius approaches large radii.
